Figures

### 2018-03-12 scripts/analysis.Rmd
fix pred plot ordering, add post hoc plots, add summary table

>>>>

```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE}

## Summary

```{r conceptual_summary, echo=FALSE}
dt <- data.frame(
  rbind(
        c("lakeconnection", "DR_Stream", "higher", "lower", "higher", "lake"), 
        c("upstream lake area", "lower", "higher", "lower", "higher", "lake"), 
        c("link_length", "lower", "higher", "lower", "higher", "stream"), 
        c("baseflow", "higher", "higher", "lower", "higher", "stream"), 
        c("stream order ratio", "higher", "higher", "lower", "higher", "stream"),
  c("upstream lake distance", "lower", "higher", "lower", "higher", "lake-stream"), 
        c("stream density", "higher", "higher", "lower", "higher", "stream")))

names(dt) <- c("metric", "direction", "k", "connectivity", "in_lake_processing", "axis")

knitr::kable(dt, caption = c("Connectivity metric effects on lake processing."))
```
